### 2021-01-06 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
on ubuntu
methodology 0

\section*{Methodology}
\label{methodology}
Methodology goes here ....

>>>>

\section*{Methodology}
\label{methodology}
Healthcare interoperability, with a focus on non-standard compliant medical schema, is dependent on the generation and validation of schema maps, as discussed above. To this end, the creation of a cohesive workflow is of utmost importance. As a possible realization of this aim, and from a purely practical point of view, our methodology is presented in the following subsections.

\subsection*{Schema acquisition}
\label{schema_acq}
In the first step of our semantic reconciliation methodology, we collect medical schema from three distinct information systems.

\subsection*{Schema preprocessing}
\label{schema_prepro}
The medical schemas and their instances are converted into an interpretable form with each attribute containining:

schema name, attribute name, min value, max value, type, semantic types[]

Methodology goes here ....
